Handbook streamFind: back end

### 2022-11-04 handbooks/Handbook_backend_streamFind.Rmd
LFU21 - tests msAnalysis and cpp extraction improvements

```{r newstreamset-basicworkflow, message=FALSE, results='hide'}
sp2 <- newStreamSet(files = files[10:21], path = getwd(), title = "Project Example")
```

>>>>

```{r newstreamset-basicworkflow, message=FALSE, results='hide'}
sp2 <- newStreamSet(files = files[10:21], title = "Project Example", run_parallel = TRUE)
```
